    \documentclass[12pt]{article}
    \usepackage{amsmath}
   
    
       \textwidth 15.5cm
       \textheight 23.0cm
       \topskip 0cm
       \evensidemargin 0.5cm     
       \oddsidemargin 0.5cm      

    \begin{document}

    \title{PHYS131 -- IT Skills -- Worksheet 3}
    \author{Samuel Hedges}
    \date{\today}
    \maketitle

    \begin{abstract}
    This is my first document typeset in \LaTeX.\textit{I declare that this submission is my own work. I have not submitted it in substantially the same form towards the award of a degree or other qualification. It has not been written or composed by any other person and all sources have been referenced or acknowledged.}
    \end{abstract}

    \tableofcontents

\section{Introduction}

In addition to the Introduction and the Summary sections, this document contains two  sections:  Equations, Sec.\ \ref{sec:Equations}, and Tables, Sec.\ \ref{sec:Table}, and their subsections.

\section{Equations}
\label{sec:Equations}

This section contains equations.
    \subsection{Quadratic equation}

$$x_{1,2} =\frac {-b^{2} \pm \sqrt{b^{2}-4ac}}{2a}$$
\textrm{This equation will give is the roots to a polynomial first order polynomial ($x_{1,2}$), if we know the coefficients of $x^{2}$, x and the y intercept which are a, b and c respectively}
    \subsection{Matrix}

This is a 3$\times$3 matrix.

$$ Q =\begin{vmatrix} 
1 & -\sigma_0^{2} & 3 \\
2 & 2 & sin(2\pi\omega_2)\\
x_1\overline{x}_2 & 3 & 1
\end{vmatrix}$$  

    \subsection{Infinite series}

As already written in my Worksheet 1 of PHYS131 -- IT Skills, the solution  of \ldots 

$$\sum_{n=0}^{\infty}\frac{1}{(1+n)^{4}} = \frac{\pi^{4}}{90} \approx 1.08232323$$
 \subsection{System of equations}

As already written in my Worksheet 1 of PHYS131 -- IT Skills, the solution  of \ldots
$$2 = a+b$$
$$a = c-b$$
$$a = b+c$$

$$a = 2, b = 0, c = 2$$
 \subsection{Indefinite integral}

 As already written in my Worksheet 1 of PHYS131 -- IT Skills, the solution  of \ldots
$$\int\frac{dx}{(1-x)^{3}}dx = \frac{1}{2(1-x)^{2}}$$


\section{Tables}
\label{sec:Table}

This section contains tables.

    \subsection{Table 1}

Here is my first table. \\
\begin{center}
\begin{tabular}{c|c}
 \hline
 \multicolumn{2}{c}{Numbers} \\
  \hline
  Even   & Odd \\ \hline
   2,4,...  & 1,3,...\\ \hline
\end{tabular}   
\end{center}

\subsection{Table 2}

Here is my second table.
\begin{center}
 \begin{tabular}{|1|c|r|}
  \hline
 & \multicolumn{2}{c|}{columns} \\ \hline
   & A & B \\ \cline{2-2}
 \hline \hline
 C & AC & BC\\ \hline
 D & AD & BD \\ \hline
 E & BE & CE \\ \hline
 \hline
 \end{tabular}
\end{center}
\section{Summary}

I have created a simple document in \LaTeX. It contains equations and tables.


    \end{document}