    \documentclass[12pt]{article}
    \usepackage{amsmath}
    \usepackage{graphicx}
    \usepackage{multirow}
    \usepackage{booktabs}
    \usepackage{subfigure}
    \usepackage{verbatim}
    \usepackage{color}
    \usepackage{hyperref}
    \usepackage{url}
    \usepackage{axessibility} 
    
    
    \begin{document}

    \title{Phys 132 -- Worksheet 2 -- 30868664}
    \author{Samuel Hedges}
    \date{\today}
    \maketitle

\section{Activity 1.}
The second book that comes up under atomic physics is: JA Alonso. Structure and properties of atomic nanoclusters. London: Imperial College London; 2005
\\
The fourth book that comes up under atomic physics is: L Banyai, SW Koch. Semiconductor and quantum dots. Singapore, River Edge NJ: World scientific; 1993
\section{Activity 2}
The second Book's class mark is BGP and can be found on A floor
\\
The Fourth Book's class mark is BGPJ and can be found on A floor
\section{Activity 3}
In Chapter one of Lipids and Nanotechnology [Mogis UA. Lipids and Nanotechnology. Urbana IL: AOCS Press; 2012] 'Richard Feynman's Pioneering lecture entitled "There's plenty of room at the Bottom"' is mentioned and was first given in 1959.
\section{Activity 4}
The first three references that come up when you search Thermoelectricity areas follows:\\
1) R Hussein, M Governale, S Kohler, W Belzig, F Glazotto, A Braggio. Nonlocal thermoelectricity in a Cooper-pair splitter. Phys Rev B. 2019-02; 99\\
2) K Yamamoto, A Aharony, O Entin-Wohlman, N Hatano. Thermoelectricity near Anderson localization transitions. Phys Rev B. 2017; 10:15-17\\
3) V Tayari, BV Senkovskiy, D Rybkovskiy, N Ehlen, A Fedorov CY Chen, J Avila. Quasi-two-dimensional thermoelectricty in SnSe. Phys Rev B.2010; 10
\section{Activity 5}
Shiogai, Y., Stefanovska, A., McClintock, P.V.E..
(2010) Nonlinear dynamics of cardiovascular ageing. Physics reports 488 (2/3), 51-110 Has been cited 247 times according to Google scholar and 187 on web of knowledge
\section{Activity 6}
A Book which may help us in our degree is J Brick, N Wilson, D Wong, M Herke. Achedemic Sucess: a student's guide to studying at university. London:Red Globe Press; 2019
\end{document}